---
title: "Mem2Att_Study_Analyses_RA"
output: html_document
---

Path for files:
/oak/stanford/groups/awagner/marcharr/MU4/study_files/

*If you don't have these packages on your computer make sure to down them first*

```{r}
# load packages
library(lme4)
library(emmeans)
library(tidyverse)

```

*This allows you to set a clear background for plots*

```{r}
theme_set(theme_classic() +
            theme(text = element_text(size = 12)))
```

*load datasets into a dataframe*

```{r}
## set path
curr_dir = '/Users/madisonhunt/Desktop/Oak/MU4/study_files'
setwd(curr_dir)
file_list <- list.files(curr_dir,  pattern = '*.txt')

data = data.frame()

for (x in 1:length(file_list)){
  temp <- read.delim(file_list[x])
     if (grepl('study1study', file_list[x], fixed=TRUE)){
            temp$StudyRep = 1
     }
   if (grepl('study2study', file_list[x], fixed=TRUE)){
            temp$StudyRep = 2
   }
   if (grepl('study3study', file_list[x], fixed=TRUE)){
            temp$StudyRep = 3
    }
    if (grepl('study4study', file_list[x], fixed=TRUE)){
            temp$StudyRep = 4
    }
  data <- rbind(data, temp)
  x=x+1
}

print(data) 

```



*Produce the median RT for each run*

```{r}
##median RT for all subject for each run (ASER)
RT_run1 <- subset(data, data$StudyRep == 1, c(SubjNum, RT))
med_RT1 = median(RT_run1[,2])
print(med_RT1)

RT_run2 <- subset(data, data$StudyRep == 2, c(SubjNum, RT))
med_RT2 = median(RT_run2[,2])
print(med_RT2)

RT_run3 <- subset(data, data$StudyRep == 3, c(SubjNum, RT))
med_RT3 = median(RT_run3[,2])
print(med_RT3)

RT_run4 <- subset(data, data$StudyRep == 4, c(SubjNum, RT))
med_RT4 = median(RT_run4[,2])
print(med_RT4)
```


```{r}
##median RT, ASER, for only correct trials
RT_run1 <- subset(data, (data$StudyRep == 1 & (data$Accuracy== 'correct Present' | data$Accuracy == 'correct Absent')), c(SubjNum, StudyRep, StudyCateg, RT))
med_RT1 = median(RT_run1[,2])
print(med_RT1)

RT_run2 <- subset(data, (data$StudyRep == 2 & (data$Accuracy== 'correct Present' | data$Accuracy == 'correct Absent')), c(SubjNum, StudyRep, StudyCateg, RT))
med_RT2 = median(RT_run2[,2])
print(med_RT2)

RT_run3 <- subset(data, (data$StudyRep == 3 & (data$Accuracy== 'correct Present' | data$Accuracy == 'correct Absent')), c(SubjNum, StudyRep, StudyCateg, RT))
med_RT3 = median(RT_run3[,2])
print(med_RT3)

RT_run4 <- subset(data, (data$StudyRep == 4 & (data$Accuracy== 'correct Present' | data$Accuracy == 'correct Absent')), c(SubjNum, StudyRep, StudyCateg, RT))
med_RT4 = median(RT_run4[,2])
print(med_RT4)
```


```{r}
##median RT, for every subject for each run (ESER), for only correct trials. Note any potential outliers don't get better (decrease in RT across blocks is minimal) really high RT

RT_data1 <- data.frame()
RT_data2 <- data.frame()
RT_data3 <- data.frame()
RT_data4 <- data.frame()

for (pt in unique(data$SubjNum)){
  temp1 <- subset(data, (data$SubjNum == pt & data$StudyRep == 1 & (data$Accuracy== 'correct Present' | data$Accuracy == 'correct     Absent')), c(SubjNum, RT))
  temp2 <- pt
  temp2[2] <- median(temp1[,2])
  RT_data1 <- rbind(RT_data1, temp2)
}

for (pt in unique(data$SubjNum)){
  temp1 <- subset(data, (data$SubjNum == pt & data$StudyRep == 2 & (data$Accuracy== 'correct Present' | data$Accuracy == 'correct     Absent')), c(SubjNum, RT))
  temp2[1] <- pt
  temp2[2] <- median(temp1[,2])
  RT_data2 <- rbind(RT_data2, temp2)
}

for (pt in unique(data$SubjNum)){
  temp1 <- subset(data, (data$SubjNum == pt & data$StudyRep == 3 & (data$Accuracy== 'correct Present' | data$Accuracy == 'correct     Absent')), c(SubjNum, RT))
  temp2[1] <- pt
  temp2[2] <- median(temp1[,2])
  RT_data3 <- rbind(RT_data3, temp2)
}

for (pt in unique(data$SubjNum)){
  temp1 <- subset(data, (data$SubjNum == pt & data$StudyRep == 4 & (data$Accuracy== 'correct Present' | data$Accuracy == 'correct     Absent')), c(SubjNum, RT))
  temp2[1] <- pt
  temp2[2] <- median(temp1[,2])
  RT_data4 <- rbind(RT_data4, temp2)
}

RT_data <- merge(RT_data1, RT_data2, by = 1)
RT_data <- merge(RT_data, RT_data3, by = 1)
RT_data <- merge(RT_data, RT_data4, by = 1)
print(RT_data)

##rename columns?
```

Generate a facet grid plot for median RT for Study Category for the first run and the last run for each participant. What is the purpose of this exercise?
You should be looking for two qualities across participants
The distributions should shrink from the first study block to the last 
The median RT for each category should overlap in the last study block
Report any potential outliers (fail to meet criteria i or ii)

```{r}
## first make a new dataframe with the correct info

RT_by_categ <- subset(data, ((data$StudyRep == 1 | data$StudyRep == 4) & (data$Accuracy== 'correct Present' | data$Accuracy == 'correct     Absent')), c(SubjNum, StudyRep, StudyCateg, RT))

RT_cat <- data.frame(SubjNum = NA,
                     StudyRep = NA, 
                     StudyCateg = NA, 
                     MedianRT= NA)


for (s in unique(RT_by_categ$SubjNum)){{
  for (r in unique(RT_by_categ$StudyRep))
    for (ca in unique(RT_by_categ$StudyCateg)) {
     temp3 <- subset(RT_by_categ, (RT_by_categ$StudyCateg == ca & RT_by_categ$StudyRep == r & RT_by_categ$SubjNum == s), c(RT))
     temp4 <- c(s, r, ca, (median(temp3[2, ])))
     RT_cat <- rbind(RT_cat, temp4)

    }
  }
}

RT_cat$MedianRT <- as.numeric(RT_cat$MedianRT)
print(RT_cat)
```


```{r}
# create graph
RT_A <- subset(RT_cat, RT_cat$StudyCateg == 'A', c(SubjNum, StudyRep, MedianRT)) 
print(RT_A)
ggplot(data=RT_A, aes(x= StudyRep, y= MedianRT, group=SubjNum)) +
         geom_line() +
         geom_point()

RT_S <- subset(RT_cat, RT_cat$StudyCateg == 'S', c(SubjNum, StudyRep, MedianRT)) 
print(RT_S)
ggplot(data=RT_S, aes(x= StudyRep, y= MedianRT, group=SubjNum)) +
         geom_line() +
         geom_point()

RT_F <- subset(RT_cat, RT_cat$StudyCateg == 'F', c(SubjNum, StudyRep, MedianRT)) 
print(RT_F)
ggplot(data=RT_F, aes(x= StudyRep, y= MedianRT, group=SubjNum)) +
         geom_line() +
         geom_point()
```

Looks at the median RT for object quadrant for Study block 1-4
Obj quadrant 1-4 correspond to four squares that partition the scene space into a cartesian plane. Obj quadrant 5 is the center of the screen.
Think through what trends should be present for each block. Report any potential outliers. 

```{r}
## create data frame

RT_quad <- subset(data, data$Accuracy== 'correct Present' | data$Accuracy == 'correct Absent', c(SubjNum, StudyRep, StudyCateg, ObjQuadrant, RT))

med_RT_quad <- data.frame(SubjNum = NA, 
                          StudyRep = NA, 
                          ObjQuadrant = NA, 
                          RT= NA )

for (s in unique(RT_quad $SubjNum)){{
  for (r in unique(RT_quad $StudyRep))
    for (q in unique(RT_quad $ObjQuadrant)) {
     temp5 <- subset(RT_quad , (RT_quad $ObjQuadrant == q & RT_quad $StudyRep == r & RT_quad $SubjNum == s), c(RT))
     temp6 <- c(s, r, q, (median(temp5[2, ])))
     med_RT_quad <- rbind(med_RT_quad, temp6)

    }
  }
}

print(med_RT_quad)
```
```{r}
## now make graphs

RT_quad0 <- subset(med_RT_quad, med_RT_quad$ObjQuadrant == 0, c(SubjNum, StudyRep, ObjQuadrant, RT))
ggplot(RT_quad0, aes(x=StudyRep, y = RT, group = SubjNum)) +
  geom_line() +
  geom_point()

RT_quad1 <- subset(med_RT_quad, med_RT_quad$ObjQuadrant == 1, c(SubjNum, StudyRep, ObjQuadrant, RT))
ggplot(RT_quad1, aes(x=StudyRep, y = RT, group = SubjNum)) +
  geom_line() +
  geom_point()

RT_quad2 <- subset(med_RT_quad, med_RT_quad$ObjQuadrant == 2, c(SubjNum, StudyRep, ObjQuadrant, RT))
ggplot(RT_quad2, aes(x=StudyRep, y = RT, group = SubjNum)) +
  geom_line() +
  geom_point()

RT_quad3 <- subset(med_RT_quad, med_RT_quad$ObjQuadrant == 3, c(SubjNum, StudyRep, ObjQuadrant, RT))
ggplot(RT_quad3, aes(x=StudyRep, y = RT, group = SubjNum)) +
  geom_line() +
  geom_point()

RT_quad4 <- subset(med_RT_quad, med_RT_quad$ObjQuadrant == 4, c(SubjNum, StudyRep, ObjQuadrant, RT))
ggplot(RT_quad4, aes(x=StudyRep, y = RT, group = SubjNum)) +
  geom_line() +
  geom_point()
```

Next, looks at values for each subject, filter by correct trials for study block 1 and block 4, then:
look at median RT, standard deviation (sd), mean RT
look at the difference between median and mean values for block 1 vs. block 4...what do you see

```{r}
RT_sub_data_all <- subset(data, (data$StudyRep == 1 | data$StudyRep ==4) & (data$Accuracy == 'correct Present' | data$Accuracy == 'correct Absent'), c(SubjNum, StudyRep, RT))


RT_sub_data <- data.frame(SubjNum= NA,
                          StudyRep = NA,
                          mean_rt= NA,
                          median_rt = NA, 
                          sd_rt = NA)

for (s in unique(RT_sub_data_all$SubjNum)){
  for (r in unique(RT_sub_data_all$StudyRep)){
    temp <- subset(RT_sub_data_all, RT_sub_data_all$SubjNum == s & RT_sub_data_all$StudyRep == r, c(RT))
    ## something is wrong because mean & median are the same and SD isn't working
    mean_temp <- mean(temp[,1], na.rm = TRUE)
    median_temp <- median(temp[,1], na.rm = TRUE)
    sd_temp <- sd(temp[,1], na.rm = TRUE)
    info_temp <- data.frame(SubjNum= s,
                          StudyRep = r,
                          mean_rt= mean_temp,
                          median_rt = median_temp, 
                          sd_rt = sd_temp)
    
    RT_sub_data <- rbind(RT_sub_data, info_temp)
  }
}

print(RT_sub_data)

ggplot(data=subset(RT_sub_data, (RT_sub_data$StudyRep == 1 | RT_sub_data$StudyRep == 4)), aes(x= StudyRep, y=median_rt, group = SubjNum))+
  geom_line()+
  geom_point()

ggplot(data=subset(RT_sub_data, (RT_sub_data$StudyRep == 1 | RT_sub_data$StudyRep == 4)), aes(x= StudyRep, y=mean_rt, group = SubjNum))+
  geom_line()+
  geom_point()

```

then calculate the upper threshold for outliers (3 SD + above) the mean and median
Save this file that contains all of values above per subject (i.e. median_RT,  mean_RT, SD, upper_med(3SD+median), upper_mean(3SD+mean)
```{r}

for (s in unique(RT_sub_data$SubjNum)){
  upper_med <- RT_sub_data$median_rt + RT_sub_data$sd_rt * 3
  RT_sub_data$upper_med <- upper_med
  upper_mean <- RT_sub_data$mean_rt + RT_sub_data$sd_rt * 3
  RT_sub_data$upper_mean <- upper_mean
}

print(RT_sub_data)

write.csv(RT_sub_data, '/Users/madisonhunt/Documents/Data/RT_sub_data.csv')
```


Then subset the DF into two separate DFs for block 1 and block 4 for correct trials only 
combine this with the newly saved file that contains upper_med, upper_mean
Then create 4 DFs
Study block 1 threshold by upper_med, upper_mean
Study block 4 threshold by upper_med, upper_mean

```{r}

```

*Plot histogram of correct responses for each study run + median x-intercept*

```{r}
c_RT_run1 <- subset(data, data$StudyRep == 1 & (data$Accuracy == 'correct Present' | data$Accuracy == 'correct Absent'), c(RT))
c_RT_run2 <-subset(data, data$StudyRep == 2 & (data$Accuracy == 'correct Present' | data$Accuracy == 'correct Absent'), c(RT))
c_RT_run3 <-subset(data, data$StudyRep == 3 &(data$Accuracy == 'correct Present' | data$Accuracy == 'correct Absent'), c(RT))
c_RT_run4 <-subset(data, data$StudyRep == 4 &(data$Accuracy == 'correct Present' | data$Accuracy == 'correct Absent'), c(RT))

hist(c_RT_run1[,1])
 abline(v=med_RT1)
hist(c_RT_run2[,1])
  abline(v=med_RT2)
hist(c_RT_run3[,1])
  abline(v=med_RT3)
hist(c_RT_run4[,1])
  abline(v=med_RT4)
```

*Plot histogram of correct repose for each object category + median x-intercept*

```{r}
c_RT_A <- subset(data, data$StudyCateg == 'A' & (data$Accuracy == 'correct Present' | data$Accuracy == 'correct Absent'), c(RT))
c_RT_F <-subset(data, data$StudyCateg == 'F' & (data$Accuracy == 'correct Present' | data$Accuracy == 'correct Absent'), c(RT))
c_RT_S <-subset(data, data$StudyCateg == 'S' &(data$Accuracy == 'correct Present' | data$Accuracy == 'correct Absent'), c(RT))

med_RT_A <- median(c_RT_A[, c(1)])
med_RT_F <- median(c_RT_F[, c(1)])
med_RT_S <- median(c_RT_S[, c(1)])



hist(c_RT_A[,1])
 abline(v=med_RT_A)
hist(c_RT_F[,1])
  abline(v=med_RT_F)
hist(c_RT_S[,1])
  abline(v=med_RT_S)

```

*Get table for responses (both incorrect and correct)* 
*then split by study rep (i.e. run)*
*then for study category overall*

```{r}
resp <- subset(data, select = c(StudyCateg, StudyRep, Accuracy))
print(resp)

resp_run1 <- subset(resp, resp$StudyRep == 1)
print(resp_run1)
resp_run2 <- subset(resp, resp$StudyRep == 2)
print(resp_run2)
resp_run3 <- subset(resp, resp$StudyRep == 3)
print(resp_run3)
resp_run4 <- subset(resp, resp$StudyRep == 4)
print(resp_run4)

resp_A <-subset(resp, resp$StudyCateg == 'A')
print(resp_A)
resp_F <-subset(resp, resp$StudyCateg == 'F')
print(resp_F)
resp_S <-subset(resp, resp$StudyCateg == 'S')
print(resp_S)
  
```